### 2015-04-30 Workshop2015/toSubmit/introduction.tex
More changes on introduction

To better understand our problem, consider a massive open online course system (MOOC) where users produce and consume content according to the geographic area and expertise of participants. 
Producers are characterized according to their location, the type and topic of the content that they can provide, the access conditions (e.g. cost, inscription, or exchange unit), and the time window in which they can produce contents. 
Consumers are described by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay, or the resources they are ready to provide in order to get the service, and QoS requirements such as availability and how critical it is to consume a given type of content. 
The MOOC  aims at being privacy respectful of the students participating in courses.
 Providers  and consumers can ask to minimize the transfer of personal data  when they share/consume content.  According to the level of trust associated to data providers, the MOOC can use privacy preserving technics to let users share content anonymously  (Constraint1). Furthermore,  data providers could  also wish to give restricted data access credentials w.r.t. to their own, when their data are used  within  an integration process (Constraint 2).

@@

  From this scenario we identify a set of issues that have to be addressed. First, how can the user efficiently obtain  results for her queries such that they meet her QoS requirements while respecting her subscribed contracts with the involved cloud provider(s)?  The user knows the low-level clauses of her SLA contract but she does not have an idea about the resources required to satisfy her requirements (SLA exported by services, example of Constraint 1).  Second, data services contracts should not be neglected in an integration process (Constraint 2).   As data services are deployed in a multi-cloud context, there is a need to establish the rules on how integration can be made and in which conditions. In fact, integration could be sometimes realized enforcing all specified conditions; we can also expect situations where they can be verified partially. In any case, how should the results of  such a  complex process  be capitalized for further integration requests?

This paper introduces a preliminary solution addressing the issues described above.  Our solution is SLA-guided: We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.  Thanks to an extended query rewriting process, a new kind of SLA is derived to match user preferences with low level agreed SLAs exported by services. The derived SLA allows to choose  services (w.r.t user demands) that can contributed for answering a query. Once data services have been chosen, the integration process will be guided by an integration SLA, negotiated taking into account user requirements and inter-cloud contracts.
%  Particularly, for queries that call several services deployed  on different clouds. 
%  Among them first,Furthermore, for a non specialist user, she do not realize what is the level of ressources she need to apply the encryption level asked  for. 
%  As data services are deployed in a multi-cloud context, there is a need to establish the rules on how integration can be made. 
%  concerns the context in which data will be used among clouds when data services are deployed in a multi-cloud configuration. How can the specified services requirements be enforced? And finally, data integration in this context faces an heterogeneity problem at different levels but specially in the scenario we are interested in, in data deployment conditions, the SLA expression language, the level security is taken into account in SLA contract.

>>>>

To better understand our problem, consider a massive open online course system (MOOC) where users produce and consume content according to the geographic area and the expertise of participants. 
Producers are characterized according to their location, the type and topic of  content  they can provide, the access conditions (e.g. cost, inscription, or exchange unit), and the time window in which they can produce content. 
Consumers are characterized by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay consuming content, or the resources they are ready to provide in order to get the service, and QoS requirements such as availability and how critical it is to consume a given type of content. Both producers and consumers have subscriptions to different cloud providers for dealing with contents exchange.
The MOOC  aims at being privacy respectful of the producers and consumers participating in courses.
 Providers  and consumers can ask to minimize the transfer of personal data  when they share/consume content.  According to the level of trust associated to data providers, the MOOC can use privacy preserving technics to let users share content anonymously  (Constraint1). Furthermore,  data providers can  also wish to give restricted data access credentials w.r.t. to their own, when their data are used  within  an integration process (Constraint 2).

@@

  From this scenario we identify a set of issues that have to be addressed. First, how can the user efficiently obtain  results for her queries such that they meet her QoS requirements while respecting her subscribed contracts with the involved cloud provider(s)?  The user knows the low-level clauses of her SLA contract but she does not have an idea about the resources required to satisfy her requirements (SLA exported by services, example of Constraint 1).  Second, data services contracts should not be neglected in an integration process (Constraint 2).   As data services are deployed in a multi-cloud context, there is a need to establish the rules on how integration can be made and in which conditions. In fact, integration could be sometimes realized enforcing all specified conditions; we can also expect situations where they can be verified partially. In any case, how should the results of  such a  complex process  be capitalized for further integration requests? The first step is to propose an architecture that integrates all services participating in a data integration process that copes QoS and SLA's of the services that participate in this process for computing a result for a given query.

 We have proposed such architecture in \cite{ghediraetal2014}. With this architecture it is necessary to revisit the specification of the integration phases in order to show how to include QoS and SLA and thereby proposing a new way of dealing with a data production and consumption process. 
Therefore, this paper introduces a preliminary solution addressing the issues described above.  Our solution is SLA-guided: We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.  Thanks to an extended query rewriting process, a new kind of SLA is derived to match user preferences with low level agreed SLAs exported by services. The derived SLA allows to choose  services (w.r.t user demands) that can contributed for answering a query. Once data services have been chosen, the integration process will be guided by an integration SLA, negotiated taking into account user requirements and inter-cloud contracts.
%  Particularly, for queries that call several services deployed  on different clouds. 
%  Among them first,Furthermore, for a non specialist user, she do not realize what is the level of ressources she need to apply the encryption level asked  for. 
%  As data services are deployed in a multi-cloud context, there is a need to establish the rules on how integration can be made. 
%  concerns the context in which data will be used among clouds when data services are deployed in a multi-cloud configuration. How can the specified services requirements be enforced? And finally, data integration in this context faces an heterogeneity problem at different levels but specially in the scenario we are interested in, in data deployment conditions, the SLA expression language, the level security is taken into account in SLA contract.
